An Integration of Multiple Constraints in ACG

### 2013-07-16 lenls/abstract.tex
Swapped Systems of ACGs with Multiple Ling Cons

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/double-acg.pdf}
    \caption{\label{fig:acg-comp-basic} Connecting form with meaning.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/serial-over-parallel.pdf}
    \caption{\label{fig:acg-comp-constr} Adding a constraint.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/parallel-over-serial.pdf}
    \caption{\label{fig:acg-comp-sem} Distinguishing syntactic and
      semantic ambiguities..}
  \end{subfigure}
  \caption{\label{fig:acg-comp} Diagrams of systems of ACGs.}
\end{figure*}

@@

This difference in syntactic behavior between noun phrases that contain
a negative determiner and those that do not has implications for our
grammar. Since two terms having an identical type in an ACG signature
can be freely interchanged in any sentence, we are forced to assign two
different types to these two different kinds of noun phrases.

@@

If we were to use this approach to write a grammar that enforces
multiple constraints at the same time, we would end up with complicated
types like the one below which provide complete specifications of the
various possible situations.

@@

This creates two problems. Firstly, the number of such types grows
exponentially with the number of features added. This can be fixed by
introducing dependent types into the type system as in
\cite{de2007type}. Secondly, and perhaps more importantly, we have lost
the clarity and simplicity of describing the individual phenomena
independently. This makes adding new constraints more and more
cumbersome and reduces our capability to reason about our grammar. It no
longer becomes apparent which language mechanisms behave independently
and their interactions are hard to track. We firmly believe that
simplicity is a fundamental requirement for constructing a large and
robust grammar and our proposal aims to reclaim that simplicity.

In our grammar, we would like to combine both of the patterns on
Figures~\ref{fig:acg-comp-constr} and \ref{fig:acg-comp-sem} and
furthermore, to use the pattern of Figure~\ref{fig:acg-comp-constr}
multiple times to implement multiple constraints independently. However,
these combinations are not possible in the framework of ACGs without
introducing complexity such as contaminating the syntax-semantics
interface by the implementation details of the syntactic layer.

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/double-acg.pdf}
    \caption{\label{fig:acg-comp-basic} Connecting form with meaning.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/serial-over-parallel.pdf}
    \caption{\label{fig:acg-comp-constr} Adding a constraint.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/parallel-over-serial.pdf}
    \caption{\label{fig:acg-comp-sem} Distinguishing syntactic and
      semantic ambiguities.}
  \end{subfigure}
  \caption{\label{fig:acg-comp} Diagrams of systems of ACGs.}
\end{figure*}

@@

This difference in syntactic behavior between noun phrases that contain a
negative determiner and those that do not has implications for our
grammar. Since two terms that have an identical type in an ACG signature can
be freely interchanged in any sentence, we are forced to assign two different
types to these two different kinds of noun phrases.

@@

If we were to use this approach to write a grammar that enforces multiple
constraints at the same time, we would end up with complicated types, like the
one below, which provide complete specifications of the various possible
situations.

@@

This creates two problems. Firstly, the number of such types grows
exponentially with the number of features added. This can be fixed by
introducing dependent types into the type system as in
\cite{de2007type}. However, secondly, and perhaps more importantly, we have
lost the clarity and simplicity of describing the individual phenomena
independently. This makes adding new constraints more and more cumbersome and
reduces our capability to reason about our grammar. It no longer becomes
apparent which language mechanisms behave independently and their interactions
are hard to track. We firmly believe that simplicity is a fundamental
requirement for constructing a large and robust grammar and our proposal aims
to reclaim that simplicity.

In our grammar, we would like to combine several constraints
(Figure~\ref{fig:acg-comp-constr}) and possibly to also separate the syntactic
ambiguities from the purely semantic ones (Figure~\ref{fig:acg-comp-sem}).
However, these combinations are not possible in the framework of ACGs without
introducing complexity by solving all the constraints in one single type
signature (the consequences of we saw above) or contaminating the
syntax-semantics interface by the implementation details of the syntactic
layer.
